---
title: "LDA_QDA_Example"
author: "STAT380"
date: '2023-10-12'
output:
  word_document: default
  html_document: default
  pdf_document:
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading the Iris Data

```{r cars}
### Example 1: Iris data
library(MASS)
library(ggplot2)
data("iris")
str(iris)
head(iris)

```

# Basic plots to see the interrelation between the variables

```{r }
pairs(iris[1:4],
             gap = 0,
             bg = c("red", "green", "blue")[iris$Species],
             pch = 21)

```

# Splitting the Data in Training and Testing Set

```{r }
set.seed(134)
ind = sample(2, nrow(iris), replace = TRUE, prob = c(0.6, 0.4))
training = iris[ind==1,]
testing = iris[ind==2,]
```

# Fitting a Linear Discriminant Analysis

```{r }
iris_lda = lda(Species~., training)
iris_lda
attributes(iris_lda); ##or 
names(iris_lda)
```

# Predicting the classes (In Training Set) based on the LDA fit

```{r }
p = predict(iris_lda, training)
library(klaR) # for the function `partimat'
partimat(Species~., data = training, method = "lda")


### Confusion matrix and accuracy – training data
p1 = predict(iris_lda, training)$class
tab = table(Predicted = p1, Actual = training$Species)
tab

```

# Predicting the classes (In Testing Set) based on the LDA fit

```{r }
p2 = predict(iris_lda, testing)$class
tab1 = table(Predicted = p2, Actual = testing$Species)
tab1

```

# QDA (Quadratic discriminant analysis on the IRIS Data)

```{r }
##Everything is not linear – quadratic discriminant analysis

iris_qda=qda(Species~.,data=training)
iris_qda
summary(iris_qda)
#library(klaR)
partimat(Species~.,data=training,method="lda")
partimat(Species~.,data=training,method="qda")

```

## Check the accuracy of our analysis of QDA in Training Set

```{r }

#Check the accuracy of our analysis of qda
Predictions_qda=predict(iris_qda,training)
table(Predictions_qda$class, training$Species)

```

## \## Check the accuracy of our analysis of QDA in Testing Set

```{r }

#Check the accuracy of our analysis of qda
Predictions_qda=predict(iris_qda,testing)
table(Predictions_qda$class, testing$Species)

```
