---
title: "Assignment2_Ans"
author: "STAT380"
date: '2023-10-29'
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r }
###
library(tree)
###
library(ISLR)
data(Carseats)
attach(Carseats)
```
The data set `Carseats' is a simulated data set containing sales of child car seats at 400 different stores of a specific departmental store over a period of a few months.  For the different activities in this assignment, we consider a categorical binary variable, that we call 'High_Sells'.  We consider the sales amount is high, i.e., High_sell=1,  if the number of  car sets that are sold is greater then 8 in the particular store. 

# Problem A
### A1.  Create a new binary categorical variable called `High_Sells' which is defined as follows: 
$ \text{High_Sales}=1 \text{ if } `Sales'>8 $ and $ \text{High_Sales}=0 \text{ if } `Sales'\leq 8 $

### A2. Add the new variable to the dataset `Carseats'.
```{r }
### A1.


### A2.

```


### A3. Build a classification tree where the response is 'High_Sells' and the predictors are all the other variables except 'Sales' and 'High-Sales'.
```{r }
### A3.

```
###

### A4. Plot the fitted tree and describe the different classification region. 
```{r }
### A4.

```


### A5.1. Now, for the cross-validation, use a training   and a validating set (200 observations in training set and the rest in the validation set). 
### A5.2. Comment on the validation part. 

```{r }
#### A5.1:



### A5.2.



```

### A6.1: Use the `cv.tree' function for the cross-validation. 
####A6.2.: Compare the obtained results with that of the  A5.2

###
```{r }
### A6.1: 

### A6.2: 

```

### A7. Plot the error rate from the cross-validation as a function of both size and k.
```{r }
### A7.

```
###

### A8. Prune the tree the best size (number of nodes) found in question 7. 

###

### A9. Predict with the pruned tree. Write a Conslusion of your finding
```{r }
### A9.

## Write a Conslusion of your finding

```

###

### A10. Compare the classification performance of the tree and the pruned tree.
```{r }
#

```



# Problem B (Fitting Regression Trees)

### We will use the regression trees for the Boston Housing data


## B1. Train a regression tree on the half of the observations of the Boston housing data. Comment no the Result.


```{r }
##

```

## B2. Plot the tree.

```{r }
##

```
###

## B3. Run the cross-validation for the tree and plot the errors.

```{r }
##

```
###

## B4. Prune the regression tree to find the optimal number of nodes.

```{r }
##

```
###

## B5. Plot the predicted values vs the test values and calculate the MSE. Comment on the obtained results.


```{r }
##

```