---
title: "RegressionDiagonistics"
author: "Subhadip Pal"
date: '2023-09-12'
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Read the Data From Appropriatew Folder 
Name of the Dataset: "Houseprice.csv"
1) Read the Data set to R workspace and call it by the name 'hp'
2) Remove the rows that has missing values. 

```{r}
hp <- read.csv(, header= ?)

# To remove all the rows that has  NA values in any one of the columns
hp <- na.omit(hp)
```

## Create a Scatter plots of the data. X variable= CrimeRate, Y Variable= HousePrice
Note: The attach command makes the variable available in the workspace.

```{r }
attach(hp) # This attach() function loads the variable in the R workspace. This is not a mandetory command. For Example, instead of attach we can simply try hp$CrimeRate. However if we do attach(hp) then the varibale   CrimeRate is also available 
plot(?,? , col="blue", pch=20, xlab="Crime Rate", ylab="House Price")

```



## Fit a Linear Reghression Model 
The command/function to fit a linear regression model is lm(). Create a model fit object: model.1. Y variable is:HousePrice, X variable is:CrimeRate

Prepare a summary of the model.1
Prepare a scatterplot (code included)
The command abline created the fitted line plot 

```{r }
model.1 <- lm(? ~ ?) # This fits the Linear Regression HousePrice= \beta_0+ \beta_1 *CrimeRate 
summary(model.1)
# summary command prints summary of all the data points. 


plot(CrimeRate, HousePrice, col="blue", pch=20, xlab="Crime Rate", ylab="House Price")
# In the plot function change pch to 21 
abline(model.1,col="dark red")
```


### Residual plot for the mode

```{r }
Residuals <- residuals(model.1)
plot(CrimeRate, Residuals, pch=20)
abline(h=0, col="dark red", lty=2)

```


# The diagonistics plots are provided Below. Simply need to type plot() and input the name of the model object; Here it is model.1

```{r }

plot(model.1)
```

We have observed that there is an influential point in the data. hence we remove the influential point for further analysis. 




# A second Fit Remiving the Influential Points
We will discuss in Class what attach and detach command does.  
Fit model.2 after removing the 62 nd row, that pertains to the incluential point. 


```{r }


hp.new <- hp[-62,]
dim(hp.new)
detach(hp)
attach(hp.new)

model.2=lm(hp.new$HousePrice~hp.new$CrimeRate)
plot(CrimeRate, HousePrice, col="blue", pch=20, xlab="Crime Rate", ylab="House Price")
abline(model.1,col="dark red", lty=2)
abline(model.2,col="dark red")


#model.2 <- lm(HousePrice~CrimeRate, data=hp.new)
summary(model.2)

```
```{r }
plot(CrimeRate, HousePrice, col="blue", pch=20, xlab="Crime Rate", ylab="House Price")
abline(lm(HousePrice~CrimeRate),col="dark red")

Residuals <- residuals(model.2)
plot(CrimeRate, Residuals, pch=20)
abline(h=0, col="dark red", lty=2)


```


### Plotting regression diagonistics for the model.2 

```{r }
plot(model.2)

```
#### To test formally/statistically whether the residuals are normally distributed or not.
```{r }
shapiro.test(model.2$residuals)

```
 It appears that the residuals are not normally distributed. Hence we try a third model with a log transformation to the response Y. 


### A third model with transformed Y 
```{r }

model.3=lm(log(HousePrice)~CrimeRate, data=hp.new)
summary(model.3)


plot(CrimeRate, log(HousePrice), col="blue", pch=20, xlab="Crime Rate", ylab="House Price")
abline(model.3,col="dark red")

```

### Visual Regression diagonistics for the third model.

```{r }
plot(model.3)
```


### Testing whether the residuals for the model3 are normal. Just to remind you that the residuals incurred from model.2 was not normally distributed. 
```{r }
shapiro.test(model.2$residuals)

shapiro.test(model.3$residuals)
```




### If we consider a transformation in the Y variable, we need to be careful how to use the fitted line for the prediction. 
```{r }
predicted_log_value<-predict(model.3, list(CrimeRate=30))
predicted_Y_value= exp(predicted_log_value)
predicted_Y_value
```
