---
title: "Class Activity Trees"
author: "STAT380"
date: '2023-11-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r }
###
library(tree)
###
library(ISLR)
#attach(Carseats)
library(rattle)
library(rpart.plot)
library(RColorBrewer)
library(partykit)
```


#(Fitting Regression Trees)

### We will use the classification trees for the Boston Housing data

Load the data from the github course page using: 

```{r }
BostonHousing<-read.csv(url("https://raw.githubusercontent.com/subhadippal2019/STAT380UAEU/main/BostonHousing.csv"))
names(BostonHousing)
```

##Some notations
Some notations on the response variable and additional information on Data. Also remove the continuous response, `MEDV' as objective of this activity is to construct a Classification tree on the categorical covariate `CAT..MEDV' 
```{r }
## Classification tree using Boston Housing data: 
# Some notation and additional information on Data
head(BostonHousing)
str(BostonHousing)
BostonHousing$MEDV_Fac = factor(BostonHousing$CAT..MEDV,labels=c("Below","Above"))
BostonHousing$MEDV_Fac
# As we will be using the MEDV_Fac as categorical response, we will remove both, `CAT..MEDV' and `MEDV' to keep on the required of the data. 
BostonH=BostonHousing[,-c(13,14)] 
#We will work on the BostonH for rest of the activity
```