---
title: "Voice Classification Data"
author: "STAT380"
date: "2024-10-10"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Packages To Load 
```{r }
library(tuneR)
```



# Set The Directory Where the Data Folder Is Located
```{r }
dir_path="/Users/subhadippal/Desktop/STAT380/voice_modeling_starter-master/"
```

# Related Functions 

## Function for Extracting Features of a Single Audio File
```{r }
Extract_Sound_Feature<-function(my_audio){
  ss<-c( c(summary(my_audio@left)), SD=sd(my_audio@left))
  names(ss)=c("Min", "Q1", "Median", "Mean", "Q3", "Max", "Sd")
  return(ss)
}

```


## Function for Extracting Features from all Audio Files in a Folder
```{r }



Extract_Sound_Feature_for_AllFile<-function(FolderName,
                         dir_path,
                          details=TRUE){
  
    files_names<-list.files(paste0(dir_path,FolderName))
   val_sound_feature=NULL
  
          for(FileIndex in 1:length(files_names)){
                      file_path<-paste0(dir_path,FolderName,"/" , files_names[FileIndex])
                      sound_file<-readWave(file_path)
                      sound_feature<-Extract_Sound_Feature(sound_file)
            
                     if(!is.null(sound_feature)){val_sound_feature<-rbind(val_sound_feature, c(sound_feature))}
                     if(details){print(paste0("Sound File='",file_path, "' Loaded Succesfully. Feature Extraction complete"))}
             }

  Y=as.factor(rep(x = FolderName, dim(val_sound_feature)[1]))
  return(data.frame(Y,val_sound_feature))
}


```



## Function To Create a Training Dataset
```{r }


Create_Training_Data_Set<-function(Category1="females", Category2="males", dir_path,  rand_err=20, details=TRUE){
  #browser()
  Train_cate1<-Extract_Sound_Feature_for_AllFile(FolderName=Category1,dir_path=dir_path,  details=details)
  Train_cate2<-Extract_Sound_Feature_for_AllFile(FolderName=Category2,dir_path=dir_path,  details=details)
  data=rbind(Train_cate1, Train_cate2)
  #Y_var<-ifelse(data$Y==Category1, 1, 0)
  
  #vv<-round(runif(rand_err, 1,length(Y_var) ))
  #Y_var[vv]= 1- Y_var[vv]
  #data$Y= Y_var
  return(data)
}

```




## Function for Extracting Features for a Testing Audio File
```{r }
    Extract_Feature_Test<-function(Test_File_Loc){
                  file_path<-paste0(Test_File_Loc)
                  sound_file<-readWave(file_path)
                  sound_feature<-Extract_Sound_Feature(sound_file)
                  return(as.data.frame(t(sound_feature)))
      }

```


# Fitting a Logistic Regression model and predict the Gender from the recorded audio file

```{r }
library(tuneR)

Categories=c("males", "females")
Training_Sound_Data<-Create_Training_Data_Set(Category1 =Categories[1], Category2 = Categories[2], dir_path = dir_path, details = TRUE )


# fitting the model using a logistic regresion model Female==1
fit<-glm(Y~., data=Training_Sound_Data, family="binomial")

```


# Obtaining the predicted probability for a new file
## Testing a Female Voice Sample
```{r }
Test_File_Loc="/Users/subhadippal/Desktop/STAT380/voice_modeling_starter-master/females/1.wav"

newData_feature=Extract_Feature_Test(Test_File_Loc)
predictedProb<-predict.glm(fit, newdata=newData_feature, type="response")
paste0("The predicted probability that the selected file is:", "female","( comparing between ", paste0(Categories, collapse=" and "), ") is ", predictedProb )
predictedProb_1=data.frame(1-predictedProb, predictedProb)
colnames(predictedProb_1)=Categories
rownames(predictedProb_1)="Predicted Group Probability"
predictedProb_1
```

## Testing a Male Voice Sample
```{r }
Test_File_Loc="/Users/subhadippal/Desktop/STAT380/voice_modeling_starter-master/males/2.wav"

newData_feature=Extract_Feature_Test(Test_File_Loc)
predictedProb<-predict.glm(fit, newdata=newData_feature, type="response")
paste0("The predicted probability that the selected file is:", "female","( comparing between ", paste0(Categories, collapse=" and "), ") is ", predictedProb )
predictedProb_1=data.frame(1-predictedProb, predictedProb)
colnames(predictedProb_1)=Categories
rownames(predictedProb_1)="Predicted Group Probability"
predictedProb_1
```


