---
title: "LDA and QDA for Image Classification"
author: "STAT380"
date: ' '
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# The Package `OpenImageR' and setting the directory
```{r }
#### Horea Muresan, Mihai Oltean, Fruit recognition from images using deep learning, Acta Univ. Sapientiae, Informatica Vol. 10, Issue 1, pp. 26-42, 2018.
#install.packages("OpenImageR")
library(OpenImageR)
library(MASS)
```


## Set the Directory Location
```{r }

dir_location<-"/Users/subhadippal/Documents/Packages/STAT380UAEU/STAT380_Fruit_Data_Small/"

```

# All Functions 
## Functions Used in the Exercise
### Extracting Color Features from a single Image

```{r }
Extract_col_feature<-function(img){
    Clr1<-summary(c(img[,, 1]))[-c(1,6)]
    Clr2<-summary(c(img[,, 2]))[-c(1,6)]
    Clr3<-summary(c(img[,, 3]))[-c(1,6)]
    val<-c(Clr1,Clr2,  Clr3)  
    #browser()
    names(val)=paste0("Feature",1:length(val) )
return(val)
}


```



### Extracting Color Features from all the Images of a folder
```{r }
ExtractFeature<-function(FolderName,                  img_path_dir="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Training/",
                      details=TRUE){
   files_names<-list.files(paste0(img_path_dir,FolderName))
  val_color_feature=NULL
  
  for(FileIndex in 1:length(files_names)){
  img_path<-paste0(img_path_dir,FolderName,"/" , files_names[FileIndex])
  #print(img_path)
  img <- tryCatch(expr = {readImage(img_path)},
                  error = function(e){ 
                    # (Optional)
                    # Do this if an error is caught...
                    return(NULL)
                  }
                  )
  #browser()
  if(!is.null(img)){
  val_color_feature<-rbind(val_color_feature, c(Extract_col_feature(img)))
  }
  if(details){
  print(paste0("ImageData='",img_path, "' Loaded Succesfully. Feature Extraction complete"))}
  }
  Y=rep(x = FolderName, dim(val_color_feature)[1])
  #val_color_feature
  return(data.frame(Y,val_color_feature))
}

```


### Function to Create the Training Dataset 

```{r }

Create_Training_Data<-function(Category1="Apple Braeburn", Category2="Apple Crimson Snow",img_path_dir=img_path_dir, rand_err=20, details=TRUE){
#browser()
Train_cate1<-ExtractFeature(FolderName=Category1, details=details, img_path_dir = img_path_dir)
Train_cate2<-ExtractFeature(FolderName=Category2, details=details, img_path_dir= img_path_dir)
data=rbind(Train_cate1, Train_cate2)

Y_var<-ifelse(data$Y==Category1, 1, 0)

vv<-round(runif(rand_err, 1,length(Y_var) ))
Y_var[vv]= 1- Y_var[vv]
data$Y= Y_var
return(data)
}
```



### Function to Extract the fearture from testing set. 
```{r }
ExtractFeature_test<-function(FolderNameLoc){
  
  img_path<-paste0(FolderNameLoc)
  #print(img_path)
  img <- tryCatch(expr = {readImage(img_path)},
                  error = function(e){ 
                    # (Optional)
                    # Do this if an error is caught...
                    return(NULL)
                  }
                  )
  #browser()
  if(!is.null(img)){
  val_color_feature<- (c(Extract_col_feature(img)))
  val_color_feature=rbind(val_color_feature,val_color_feature)
  }
  
  #Y=rep(x = FolderName, dim(val_color_feature)[1])
  #val_color_feature
  return(data.frame(val_color_feature)[1,])
}

```



# Sample Images of the objects that we are considering (Just for Checking if the Folders are set correctly)

```{r } 
CategoryLabels=data.frame(Category=c("Apple Braeburn","Apple Crimson Snow" ), ResponseInd=c(1,0)) # Means Apple Braeburn===1, Apple Crimson Snow===0
img_path=paste0(dir_location, "Training/",CategoryLabels$Category[1],"/1_100.jpg")



img<-readImage(img_path)
imageShow(img)
```



```{r }
img_path=paste0(dir_location,"Training/",CategoryLabels$Category[2],"/1_100.jpg")
img<-readImage(img_path)
imageShow(img)

```



### Creating the Traininig Dataset by extracting the features by reading all the samples/images from the Data folder
```{r  }

Training_dir_location<-paste0(dir_location, "Training/")

data<-Create_Training_Data(Category1 = CategoryLabels$Category[1], Category2 =CategoryLabels$Category[2],img_path_dir =Training_dir_location,  details = FALSE)
dim(data)


```





# LDA

```{r }
library(MASS)

linearLDA_AO <- lda(Y~., data=data)
plot(linearLDA_AO)
```

```{r }
linearLDA_AO$means


#Col_infor<-ifelse(data$Y=='Orange', "Orange", ifelse(Data$Y=='Apple Braeburn', "red",ifelse(Data$Y=='Apple Granny Smith', "pink","purple" ) ) )
plot(linearLDA_AO)
```


### Predict the category of the following object
```{r }

Test_Folder_Loc= paste0(dir_location, "Test/Apple Crimson Snow/80_100.jpg")

img<-readImage(Test_Folder_Loc)
imageShow(img)


newData_feature=ExtractFeature_test(Test_Folder_Loc)
pred_LDA_AO<-predict(linearLDA_AO, newdata=newData_feature)
Pred_prob<-pred_LDA_AO$posterior
colnames(Pred_prob)=CategoryLabels$Category[c(2,1)]
rownames(Pred_prob)="Predicted Posterior Probability"
Pred_prob
```






# QDA

```{r }
#library(MASS)
Quadratic_QDA_AO <- qda(Y~., data=data)
```

```{r }
Quadratic_QDA_AO$means
```




### Precict the Category of the Following Object
```{r }

Test_Folder_Loc= paste0(dir_location, "Test/Apple Crimson Snow/80_100.jpg")

img<-readImage(Test_Folder_Loc)
imageShow(img)

newData_feature=ExtractFeature_test(Test_Folder_Loc)
pred_LDA_AO<-predict(Quadratic_QDA_AO, newdata=newData_feature)
Pred_prob<-pred_LDA_AO$posterior
colnames(Pred_prob)=CategoryLabels$Category[c(2,1)]
rownames(Pred_prob)="Predicted Posterior Probability"
Pred_prob
```



# More than Two Category Classificaion Unisng LDA and QDA

```{r }

### Function to Create the Training Dataset 

Create_Training_Data_General<-function(Categories=c("Apple Braeburn","Apple Crimson Snow"),img_path_dir=img_path_dir, rand_err=20, details=TRUE){
#browser()
Number_of_Classes_G= length(Categories)
Train_data=NULL
for( g in 1:Number_of_Classes_G ){
  Train_data_temp<-ExtractFeature(FolderName=Categories[g], details=details, img_path_dir = img_path_dir)
  Train_data=rbind(Train_data, Train_data_temp)
        
}
#Y_var<-ifelse(data$Y==Category1, 1, 0)

#vv<-round(runif(rand_err, 1,length(Y_var) ))
#Y_var[vv]= 1- Y_var[vv]
#data$Y= Y_var
return(Train_data)
}
```



```{r }
Training_dir_location<-paste0(dir_location, "Training/")
Data<-Create_Training_Data_General(Categories=c("Apple Braeburn","Apple Crimson Snow", "Orange", "Apple Granny Smith"),img_path_dir=Training_dir_location, rand_err=20, details=FALSE)

```


```{r }
lda_1<-lda(Y~., data=Data)
 

Col_infor<-ifelse(Data$Y=='Orange', "Orange", ifelse(Data$Y=='Apple Braeburn', "red",ifelse(Data$Y=='Apple Granny Smith', "pink","purple" ) ) )
#Col_infor=as.integer(as.factor(Data$Y))
plot(lda_1, cex = .5, col=Col_infor)
```


### Predict the category of the following object
```{r }

Test_Folder_Loc= paste0(dir_location, "Test/Apple Crimson Snow/80_100.jpg")

img<-readImage(Test_Folder_Loc)
imageShow(img)


newData_feature=ExtractFeature_test(Test_Folder_Loc)
pred_LDA_AO<-predict(lda_1, newdata=newData_feature)
Pred_prob<-pred_LDA_AO$posterior
rownames(Pred_prob)="Predicted Posterior Probability"
Pred_prob
```

```{r }
qda_1<-qda(Y~., data=Data)
 
```
