---
title: "AppleOrange"
author: "STAT380"
date: '2023-10-05'
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# We consider logistric regression for the binary classification. 


```{r }
#### Horea Muresan, Mihai Oltean, Fruit recognition from images using deep learning, Acta Univ. Sapientiae, Informatica Vol. 10, Issue 1, pp. 26-42, 2018.
#install.packages("OpenImageR")
library(OpenImageR)
```

## Functions Used in the Exercise

```{r }
Extract_col_feature<-function(img){
    Clr1<-summary(c(img[,, 1]))[-c(1,6)]
    Clr2<-summary(c(img[,, 2]))[-c(1,6)]
    Clr3<-summary(c(img[,, 3]))[-c(1,6)]
    val<-c(Clr1,Clr2,  Clr3)  
    #browser()
    names(val)=paste0("Feature",1:length(val) )
return(val)
}


```




```{r }
ExtractFeature<-function(FolderName,
                      img_path_dir="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Training/",
                      details=TRUE){
  #browser()
  #img_path1="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Training/Orange/0_100.jpg"
  files_names<-list.files(paste0(img_path_dir,FolderName))
  val_color_feature=NULL
  
  for(FileIndex in 1:length(files_names)){
  img_path<-paste0(img_path_dir,FolderName,"/" , files_names[FileIndex])
  #print(img_path)
  img <- tryCatch(expr = {readImage(img_path)},
                  error = function(e){ 
                    # (Optional)
                    # Do this if an error is caught...
                    return(NULL)
                  }
                  )
  #browser()
  if(!is.null(img)){
  val_color_feature<-rbind(val_color_feature, c(Extract_col_feature(img)))
  }
  if(details){
  print(paste0("ImageData='",img_path, "' Loaded Succesfully. Feature Extraction complete"))}
  }
  Y=rep(x = FolderName, dim(val_color_feature)[1])
  #val_color_feature
  return(data.frame(Y,val_color_feature))
}

```


Function to Create the Training Dataset 

```{r }

Create_Training_Data<-function(Category1="Apple Braeburn", Category2="Apple Crimson Snow", rand_err=20, details=TRUE){
#browser()
Train_cate1<-ExtractFeature(FolderName=Category1, details=details)
Train_cate2<-ExtractFeature(FolderName=Category2, details=details)
data=rbind(Train_cate1, Train_cate2)
Y_var<-ifelse(data$Y==Category1, 1, 0)

vv<-round(runif(rand_err, 1,length(Y_var) ))
Y_var[vv]= 1- Y_var[vv]
data$Y= Y_var
return(data)
}
```



### Function to Extract the fearture from testing set. 
```{r }
ExtractFeature_test<-function(FolderNameLoc){
  #img_path_dir="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Training/"
  #img_path1="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Training/Orange/0_100.jpg"

  #img_path_dir
  img_path<-paste0(FolderNameLoc)
  #print(img_path)
  img <- tryCatch(expr = {readImage(img_path)},
                  error = function(e){ 
                    # (Optional)
                    # Do this if an error is caught...
                    return(NULL)
                  }
                  )
  #browser()
  if(!is.null(img)){
  val_color_feature<- (c(Extract_col_feature(img)))
  val_color_feature=rbind(val_color_feature,val_color_feature)
  }
  
  #Y=rep(x = FolderName, dim(val_color_feature)[1])
  #val_color_feature
  return(data.frame(val_color_feature)[1,])
}

```



### Sample Images of the objects that we are considering 
```{r }
CategoryLabels=data.frame(Category=c("Apple Braeburn","Apple Crimson Snow" ), ResponseInd=c(1,0)) # Means Apple Braeburn===1, Apple Crimson Snow===0
img_path=paste0("/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Training/",CategoryLabels$Category[1],"/1_100.jpg")
img<-readImage(img_path)
imageShow(img)
```

```{r }
img_path=paste0("/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Training/",CategoryLabels$Category[2],"/1_100.jpg")
img<-readImage(img_path)
imageShow(img)

```



### Creating the Traininig Dataset by extracting the features by reading all the samples/images from the Data folder
```{r  }

#CategoryLabels=data.frame(Category=c("Apple Braeburn","Apple Crimson Snow" ), ResponseInd=c(1,0)) # Means Apple Braeburn===1, Apple Crimson Snow===0

data<-Create_Training_Data(Category1 = CategoryLabels$Category[1], Category2 =CategoryLabels$Category[2], details = FALSE)
dim(data)

#data<-Create_Train_Data(rand_err = 15, details = FALSE)
#dim(data)
```

### Fit a logistic regression with Y=Response

```{r }
fit<-glm(Y~., data=data, family="binomial")
#cbind(fit$fitted.values, data$Y)
```





### Prediction on a data from the testing set: Predict the category of the follwoing object
```{r }
FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Crimson Snow/80_100.jpg"

#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Braeburn/80_100.jpg"
img<-readImage(FolderNameLoc);imageShow(img)
#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Golden 1/63_100.jpg"

newData_feature=ExtractFeature_test(FolderNameLoc)
predictedProb<-predict.glm(fit, newdata=newData_feature, type="response")
paste0("The predicted probability that the selected image is:",CategoryLabels$Category[1],"( comparing between ", paste0(CategoryLabels$Category, collapse=" and "), ") is ", predictedProb )
predictedProb_1=data.frame(predictedProb, 1-predictedProb)
colnames(predictedProb_1)=CategoryLabels$Category
rownames(predictedProb_1)="Predicted Group Probability"
predictedProb_1
```



## APPLE AND ORNAGE Dataset

### Sample Images of the objects that we are considering 
```{r }
CategoryLabels=data.frame(Category=c("Orange","Apple Braeburn" ), ResponseInd=c(1, 0))
#Orange===1, and Apple Braeburn===0
img_path=paste0("/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Training/",CategoryLabels$Category[1],"/1_100.jpg")
img<-readImage(img_path)
imageShow(img)
```


```{r }
img_path=paste0("/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Training/",CategoryLabels$Category[2],"/1_100.jpg")
img<-readImage(img_path)
imageShow(img)

```


### Creating the Traininig Dataset by extracting the features by reading all the samples/images from the Data folder
```{r  }
#CategoryLabels=data.frame(Category=c("Orange","Apple Braeburn" ), ResponseInd=c(1, 0))
#Orange===1, and Apple Braeburn===0
data_o<-Create_Training_Data(Category1 = CategoryLabels$Category[1], Category2 =CategoryLabels$Category[2], details = FALSE)
dim(data)
```

```{r }
fit_o<-glm(Y~., data=data_o, family="binomial")
#Estimated_prob<-cbind(fit$fitted.values, data$Y)
```

### Predict the category of the following object
```{r }
FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Braeburn/80_100.jpg"
img<-readImage(FolderNameLoc);imageShow(img)
#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Orange/6_100.jpg"
#img<-readImage(FolderNameLoc);imageShow(img)

newData_feature=ExtractFeature_test(FolderNameLoc)
predictedProb<-predict.glm(fit_o, newdata=newData_feature, type="response")
paste0("The predicted probability that the selected image is:",CategoryLabels$Category[1],"( comparing between ", paste0(CategoryLabels$Category, collapse=" and "), ") is ", predictedProb )
predictedProb_1=data.frame(predictedProb, 1-predictedProb)
colnames(predictedProb_1)=CategoryLabels$Category
rownames(predictedProb_1)="Precicted Group Probability"
predictedProb_1
```


# LDA

```{r }
library(MASS)

linearLDA_AO <- lda(Y~., data=data_o)
plot(linearLDA_AO)
```

```{r }
linearLDA_AO$means
```


### Predict the category of the following object
```{r }
#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Crimson Snow/80_100.jpg"

FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Braeburn/80_100.jpg"

#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Golden 1/63_100.jpg"
#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Orange/6_100.jpg"
img<-readImage(FolderNameLoc)
imageShow(img)


newData_feature=ExtractFeature_test(FolderNameLoc)
pred_LDA_AO<-predict(linearLDA_AO, newdata=newData_feature)
Pred_prob<-pred_LDA_AO$posterior
colnames(Pred_prob)=CategoryLabels$Category[c(2,1)]
rownames(Pred_prob)="Predicted Posterior Probability"
Pred_prob
```






# QDA

```{r }
#library(MASS)
Quadratic_QDA_AO <- qda(Y~., data=data_o)
```

```{r }
Quadratic_QDA_AO$means
```




### Precict the Category of the Following Object
```{r }
#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Crimson Snow/80_100.jpg"

FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Braeburn/80_100.jpg"

#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Golden 1/63_100.jpg"
#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Orange/6_100.jpg"
img<-readImage(FolderNameLoc)
imageShow(img)

newData_feature=ExtractFeature_test(FolderNameLoc)
pred_LDA_AO<-predict(Quadratic_QDA_AO, newdata=newData_feature)
Pred_prob<-pred_LDA_AO$posterior
colnames(Pred_prob)=CategoryLabels$Category[c(2,1)]
rownames(Pred_prob)="Predicted Posterior Probability"
Pred_prob
```

```{r }

#FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Apple Braeburn/80_100.jpg"


FolderNameLoc="/Users/subhadippal/Downloads/Fruit-Images-Dataset-master/Test/Orange/6_100.jpg"
img<-readImage(FolderNameLoc);imageShow(img)
newData_feature=ExtractFeature_test(FolderNameLoc)
pred_LDA_AO<-predict(Quadratic_QDA_AO, newdata=newData_feature)
Pred_prob<-pred_LDA_AO$posterior
colnames(Pred_prob)=CategoryLabels$Category[c(2,1)]
rownames(Pred_prob)="Predicted Posterior Probability"
Pred_prob
```

