---
title: "LogisticRegressionOlingFailure"
author: "STAT380"
date: '2023-10-05'
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# O-Ring Failure Data

## The context
 The Space Shuttle Challenger crashed 73 seconds after
liftoff on January 28th, 1986. The disaster claimed the lives
of all seven astronauts on board. The details surrounding this
disaster were very involved.

"The engineers who manufactured the large boosters that
launched the rocket had data on the possible failures that could
happen during cold temperatures. They tried to prevent the
launch, but were ultimately ignored and disaster ensued."

It was known that there is an association between the ORing
seal failure and the low atmosphere temparature temperature.

 The “fail" column in the data set below records how many
O-rings experienced failures during that particular launch. The
“temp" column lists the outside temperature at the time of launch.

### The data is available at: "https://raw.githubusercontent.com/subhadippal2019/STAT380UAEU/main/oring1.csv"

```{r }
oring1<-read.csv(url("https://raw.githubusercontent.com/subhadippal2019/STAT380UAEU/main/oring1.csv"))
summary(oring1)

```


## Fit the logistic regression model:
```{r }
fit_oring<-glm(oringFail~temperature, data=oring1, family="binomial")
summary(fit_oring)
```




### predict the probability of Failure at a given atmosphere temperature

```{r }
#predict(fit_oring)
predict(fit_oring,newdata = data.frame(temperature=31))
predict(fit_oring,newdata = data.frame(temperature=31), type="response")


```